TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-10-09 paper/draft.tex
isochrone fig
more caption detail

Iron abundances ([Fe/H]) are assignied to the physical parameter sample based on the strenngth of metal-sensitive lines in the near-infrared SpeX spectra \citep{RojasAyala:2010} using the calibration from \citet{Mann:2013a}. The relation between these lines and an absolute [Fe/H] scale is calibrated using wide binaries containing and F, G, or K-type primary and an M dwarf companion, under the assumption that binaries formed from the same molecular cloud and therefore have the same metallicity \citep{Bonfils:2005}. Uncertainties are estimated to be $\simeq$0.08\,dex based on irreducable scatter in the empirical relation between selected lines and the assigned [Fe/H] from the primary star. As with \teff\ relative errors on [Fe/H] are smaller, estimated to be 0.04-0.06\,dex over most of the temperature and metallicity range considered here.

@@

\item[-] Is it interesting to point out the comoving pairs we found? (33 FGK-M, 13 WD-M, and 174 M-M pairs)?

@@

@@

>>>>

Iron abundances ([Fe/H]) are assignied to the physical parameter sample based on the strength of metal-sensitive lines in the near-infrared SpeX spectra \citep{RojasAyala:2010} using the calibration from \citet{Mann:2013a}. The relation between these lines and an absolute [Fe/H] scale is calibrated using wide binaries containing and F, G, or K-type primary and an M dwarf companion, under the assumption that binaries formed from the same molecular cloud and therefore have the same metallicity \citep{Bonfils:2005}. Uncertainties are estimated to be $\simeq$0.08\,dex based on irreducable scatter in the empirical relation between selected lines and the assigned [Fe/H] from the primary star. As with \teff\ relative errors on [Fe/H] are smaller, estimated to be 0.04--0.06\,dex over most of the temperature and metallicity range considered here.

@@

@@

Future work:
\begin{enumerate}
\item[-] Create a binary sample; using color/magnitude \citealt{Widmark:2018} and by spectroscopy \citealt{ElBadry:2018}
\end{enumerate}

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/isochrone_cmd.png}
\caption{Comparison of Cannon [Fe/H] as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (1, 3, 5, and 7 Gyr). \label{fig:isochrone_cmd}}
\end{figure}

\begin{figure}[ht]
\plotone{figures/mann_radii.png}
\caption{Comparison of radii estimated from M15 relations. \label{fig:radii}}
\end{figure}
